Automatic Hadith Graphs using Arabic Morphological Analysis

### 2011-09-19 trunk/tex/hadith.ijcnlp.tex
updated genealogy code, but still some issue in corpus present to be solved

The problem at hand has significant contribution to the general task of Named Entity Recognition (NER). It has been noted that
gazetteers play an important role in the accuracy of knowledge-based approaches and bootstrapping learning
approaches~\cite{Kozareva:06,Carlson:09,Toral:06,Benajiba:07,Kazama:08,Nadeau:06}. Nonetheless, although gazetteers result in high accuracy,
they are hard to obtain and mantain. % They are also language and domain-dependent. 
Consequently, many automatic methods have been proposed to generate extensive gazetteers instead of relying on the time-consuming manual work
to compile such lists. Proposed methods include: writing some rules for the context of the named entities targeted such as propositions that
introduce them, also known as trigger gazetteers~\cite{Kozareva:06,Toral:06}; utilizing free online encyclopedias such as Wikipedia which are 
continually mantained~\cite{Benajiba:07,Kazama:08}; in addition to reliance on web search engines starting from a small list of words and extracting
similar that appear in the extracted pages~\cite{Nadeau:06}.

>>>>

The problem at hand has significant contribution to the general task of Named Entity Recognition (NER). It has been noted that
gazetteers play an important role in the accuracy of knowledge-based approaches and bootstrapping learning
approaches~\cite{Kozareva:06,Carlson:09,Toral:06,Benajiba:07,Kazama:08,Nadeau:06}. Nonetheless, although gazetteers result in high accuracy,
they are hard to obtain and mantain. % They are also language and domain-dependent. 
Consequently, many automatic methods have been proposed to generate extensive gazetteers instead of relying on the time-consuming manual work
to compile such lists. Proposed methods include: writing some rules for the context of the named entities targeted such as propositions that
introduce them, also known as trigger gazetteers~\cite{Kozareva:06,Toral:06}; utilizing free online encyclopedias such as Wikipedia which are 
continually maintained~\cite{Benajiba:07,Kazama:08}; in addition to reliance on web search engines starting from a small list of words and extracting
similar that appear in the extracted pages~\cite{Nadeau:06}.
